---
title: "Getting Started with hyperliquid"
author: "Dereck Mezquita"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting Started with hyperliquid}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  results = "hold",
  comment = "#>",
  warning = FALSE,
  message = FALSE
)

# This vignette renders against a global httr2 mock: every request is answered
# from canned fixtures, so the examples execute and print realistic,
# deterministic data with no network, no real credentials, and no funds.
box::use(
  hyperliquid[
    HyperliquidMarketData, HyperliquidAccount, HyperliquidTrading,
    HyperliquidStaking, get_api_keys, hyperliquid_backfill_klines,
    hyperliquid_ohlcv
  ],
  coro,
  later,
  ../tests/testthat/mock_router[mock_router]
)

options(httr2_mock = mock_router)

# Signed /exchange actions sign the request body with the wallet key BEFORE the
# request is performed, so a loadable key must exist even though the mock ignores
# the signature. We use a THROWAWAY, well-known test scalar: it signs fine,
# controls no real funds, and never touches the network.
.sk_hex <- "0123456789012345678901234567890123456789012345678901234567890123"
KEYS <- get_api_keys(private_key = paste0("0x", .sk_hex))
```

This vignette walks through `hyperliquid` in **synchronous** mode: constructing a
client, fetching public market data, reading account state, and safely signing a
`/exchange` order against a mock so nothing leaves your machine.

## Disclaimer

This software is provided for educational and research purposes. Trading
cryptocurrency carries substantial risk, and you are solely responsible for any
orders, transfers, or withdrawals placed through this package. Every signed call
in this vignette runs against a mock; against the live API it would move real
funds. Test against testnet (`testnet = TRUE`) before signing anything on
mainnet.

## Installation

```{r install, eval = FALSE}
# install.packages("remotes")
remotes::install_github("dereckscompany/hyperliquid")
```

## Authentication

Public `/info` reads (market data, account state, staking reads) need no
credentials. Signed `/exchange` actions (trading, transfers, staking writes) are
authenticated by an **Ethereum wallet signature**: Hyperliquid uses no API keys,
only your wallet's secp256k1 private key.

Store the key as an environment variable in `.Renviron`:

```bash
HYPERLIQUID_PRIVATE_KEY="0x<64-hex-character-secp256k1-key>"
# Optional: the master account address when the key above is an AGENT (API)
# wallet approved to act on its behalf.
HYPERLIQUID_ACCOUNT_ADDRESS="0x<master-account-address>"
```

`get_api_keys()` reads those variables (and derives the wallet address from the
key), so in practice you simply call `HyperliquidTrading$new()` and the
credentials are picked up automatically.

```{r load, eval = FALSE}
box::use(
  hyperliquid[
    HyperliquidMarketData, HyperliquidAccount, HyperliquidTrading, get_api_keys
  ]
)

keys <- get_api_keys(
  private_key = "0x<64-hex-character-secp256k1-key>"
)
```

> **One key, one flag for the network.** The same key serves both mainnet and
> testnet. The network is selected by the explicit `testnet` argument at
> construction, never by the URL, because the network changes the signature
> itself (the phantom-agent source and the `hyperliquidChain` tag are part of
> what is signed). Pass `testnet = TRUE` to sign and route against testnet.

---

## Market Data

`HyperliquidMarketData` covers every public (no auth) `/info` read. It needs no
key.

```{r market-init}
market <- HyperliquidMarketData$new()
```

### Perpetual Metadata

The perpetual universe: every listed coin with its size decimals and max
leverage.

```{r meta}
meta <- market$get_meta()
meta[]
```

### Mid Prices

`get_all_mids()` returns the mid price for every actively traded coin, long: one
row per coin.

```{r mids}
mids <- market$get_all_mids()
mids[]
```

### OHLCV Candles

`get_candles()` returns OHLCV bars for a coin over a time range, sorted ascending
by open time. Valid intervals are in `HYPERLIQUID_INTERVALS` (`"1m"` ... `"1M"`).
Time bounds accept a POSIXct or epoch-milliseconds.

```{r candles}
candles <- market$get_candles(
  "BTC",
  interval = "1h",
  start = lubridate::now("UTC") - lubridate::days(1),
  end = lubridate::now("UTC")
)
candles[]
```

### Order Book

`get_l2_book()` returns both sides of the L2 book stacked into one long table
with a `side` discriminator and a 1-indexed `level`.

```{r book}
book <- market$get_l2_book("BTC")
book[]
```

### Recent Trades

```{r trades}
market$get_recent_trades("BTC")[, .(coin, side, px, sz, time)]
```

---

## Account State

`HyperliquidAccount` reads the full state and history of any account from `/info`
by its address. The reads are unauthenticated, so pass the address you want to
inspect (when a signing key is set, `address` defaults to your own wallet).

```{r account-init}
account <- HyperliquidAccount$new()
addr <- "0x010461c14e146ac35fe42271bdc1134ee31c703a"
```

### Positions and Margin

`get_positions()` returns one row per open perpetual position; the cross-margin
summary is a sibling method (`get_margin_summary()`) reading the same payload.

```{r positions}
account$get_positions(addr)[, .(coin, szi, entry_px, unrealized_pnl, leverage_value)]
```

```{r margin}
account$get_margin_summary(addr)[, .(account_value, total_ntl_pos, withdrawable)]
```

### Fills

```{r fills}
fills <- account$get_user_fills(addr)
fills[, .(coin, side, px, sz, dir, closed_pnl, fee)]
```

---

## Trading

`HyperliquidTrading` places, modifies, and cancels orders. Every method signs an
`/exchange` action with your wallet key. The calls below run against the mock;
against the live API they would place and cancel real orders.

```{r trading-init}
trading <- HyperliquidTrading$new()
```

```{r trading-init-hidden, echo = FALSE}
trading <- HyperliquidTrading$new(keys = KEYS)
```

### Place an Order

An order's `order_type` is either a limit
(`list(limit = list(tif = "Gtc"|"Ioc"|"Alo"))`) or a trigger order. The result
is one row per resulting status (`resting`, `filled`, or `error`):

```{r place}
order <- trading$place_order(
  "BTC",
  is_buy = TRUE,
  sz = 0.001,
  limit_px = 50000,
  order_type = list(limit = list(tif = "Gtc"))
)
order[]
```

### Cancel an Order

`cancel_order()` cancels one resting order by its order id, returning one row per
cancel:

```{r cancel}
trading$cancel_order("BTC", oid = order$oid[order$status == "resting"][1])
```

---

## Staking

`HyperliquidStaking` reads a delegator's staking state from `/info` (no key), and
delegates / undelegates the native token with a key.

```{r staking}
staking <- HyperliquidStaking$new()
staking$get_staking_summary("0x5ac99df645f3414876c816caa18b2d234024b487")
```

---

## The Data-Shape Policy

Every method returns a single flat `data.table` with **no list columns**:

- Nested API objects are flattened into scalar `snake_case` columns (e.g. a
  position's `leverage` becomes `leverage_type` and `leverage_value`).
- Endpoints that bundle two things are split into sibling methods over the same
  payload (`get_positions()` / `get_margin_summary()`).
- Heterogeneous rows are stacked with a discriminator column: the L2 book's
  `side`, an order action's `status`, a ledger's `delta_type`.
- Prices, sizes, and amounts are parsed to numeric; timestamps are `POSIXct` in
  UTC (via `lubridate`).

This means the result of any call drops straight into `data.table` joins,
`rbindlist()`, or a database write with no further unnesting.

---

## Bulk Backfill and Bundled Data

For historical collection, `hyperliquid_backfill_klines()` downloads candles for
many coins and intervals to a CSV, appending incrementally so progress survives
an interruption (re-running resumes each series from its last stored row). It
writes a file, so it is shown but not executed here:

```{r backfill, eval = FALSE}
hyperliquid_backfill_klines(
  symbols = c("BTC", "ETH"),
  intervals = c("1d", "1h"),
  from = lubridate::as_datetime("2024-01-01", tz = "UTC"),
  file = "klines.csv"
)
```

A bundled sample dataset, `hyperliquid_ohlcv`, ships daily candles for `"BTC"`,
`"ETH"`, and `"SOL"`:

```{r dataset}
head(hyperliquid_ohlcv)
```

---

## Asynchronous Use

Every class works in async mode. Pass `async = TRUE` and each method returns a
[promise][promises::promise] instead of a `data.table`. The recommended idiom is
`coro::async()` / `await()` for sequential-looking code, driving the event loop
with [later](https://r-lib.github.io/later/):

```{r async}
market_async <- HyperliquidMarketData$new(async = TRUE)

main <- coro$async(function() {
  mids <- await(market_async$get_all_mids())
  book <- await(market_async$get_l2_book("BTC"))

  print(mids)
  print(book)
  return(invisible(NULL))
})

main()

# Drain the event loop until every promise has resolved.
while (!later$loop_empty()) {
  later$run_now()
}
```

---

## Next Steps

- Browse the [pkgdown site](https://dereckscompany.github.io/hyperliquid/) for
  full method documentation.
- For bulk historical data collection, see `?hyperliquid_backfill_klines` and
  `?hyperliquid_backfill_funding`.
