---
title: "Trading Strategies: Long, Short, and Pairs Trading"
author: "Dereck Mezquita"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Trading Strategies: Long, Short, and Pairs Trading}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  results = "hold",
  comment = "#>",
  warning = FALSE,
  message = FALSE
)

# Every example runs against a global httr2 mock: requests are answered from
# canned fixtures (grounded in real testnet captures), so the document renders
# deterministically with no network, no real credentials, and no funds.
box::use(
  hyperliquid[
    HyperliquidMarketData, HyperliquidAccount, HyperliquidTrading, get_api_keys
  ],
  ../tests/testthat/mock_router[mock_router]
)
options(httr2_mock = mock_router)

# A throwaway, well-known test key: it signs fine, the mock ignores the
# signature, it controls no real funds, and it never touches the network.
KEYS <- get_api_keys(private_key = paste0("0x", strrep("0123456789", 6), "0123"))
```

This guide is for readers who are new to derivatives trading. It explains the
vocabulary as it goes and then builds up to a **market-neutral pairs trade**. All
code executes against a deterministic mock, so the printed output is real in
*shape* but moves no money. Before doing any of this for real, read the
[live testnet walkthrough](live-testnet-walkthrough.html) and practise on testnet.

> Trading leveraged derivatives is risky and can lose more than your deposit.
> Nothing here is financial advice.

## The vocabulary, in one minute

- **Spot** trading means buying and *owning* the asset (you hold the coin).
- A **perpetual future ("perp")** is a contract that tracks an asset's price
  without ever expiring. You never own the coin; you hold a *position* that gains
  or loses as the price moves. Perps are the core of Hyperliquid.
- **Long** = you profit when the price goes **up** (`is_buy = TRUE`).
- **Short** = you profit when the price goes **down** (`is_buy = FALSE`). A short
  is a first-class position, not a workaround.
- **Leverage** lets a small amount of collateral control a larger position (e.g.
  5x). It magnifies gains *and* losses, and can trigger **liquidation** (your
  position is force-closed) on an adverse move.
- **Funding** is a small payment exchanged between longs and shorts every few
  hours to keep the perp price tethered to the spot price.

## Reading the market

Market data needs no credentials.

```{r market}
md <- HyperliquidMarketData$new()

# Mid prices across all perps (one row per coin).
head(md$get_all_mids(), 4)

# The order book for BTC: bids and asks stacked long, with a `side` column.
head(md$get_l2_book("BTC"), 4)
```

## Opening a position, and the order types

`HyperliquidTrading` signs and sends orders. The two everyday order types:

- **Limit order** — rests on the book at a price you choose; fills only at that
  price or better. Its **time-in-force** controls how it lives:
  `"Gtc"` (good-til-cancelled, the default), `"Ioc"` (immediate-or-cancel — fill
  now or die), `"Alo"` (add-liquidity-only / post-only — never crosses the spread).
- **Market order** — fills immediately by crossing the spread (`market_open()`
  implements this as an aggressive IOC).

```{r long}
trading <- HyperliquidTrading$new(keys = KEYS)

# A good-til-cancelled limit BUY (a long): rest a bid at 60,000.
trading$place_order(
  name = "BTC", is_buy = TRUE, sz = 0.001, limit_px = 60000,
  order_type = list(limit = list(tif = "Gtc"))
)

# Or take liquidity immediately with a market buy.
trading$market_open(name = "BTC", is_buy = TRUE, sz = 0.001)
```

## Going short

Selling a perp you do not hold *opens a short* -- you are now positioned to profit
if the price falls. The only change is `is_buy = FALSE`.

```{r short}
# A market SHORT on ETH.
trading$market_open(name = "ETH", is_buy = FALSE, sz = 0.05)
```

## Leverage and margin

Set the leverage per market before sizing up. **Cross** margin shares collateral
across all positions; **isolated** margin walls off a single position so a
liquidation there cannot drain the rest.

```{r leverage}
# 5x cross-margin leverage on BTC.
trading$update_leverage(name = "BTC", leverage = 5, is_cross = TRUE)
```

## Pairs trading (market-neutral)

This is the strategy that motivated the example. A **pairs trade** holds **one leg
long and one leg short** at the same time -- so you profit from the *relative*
move between the two, not the market's overall direction. If you are long BTC and
short ETH and BTC outperforms ETH, you win **even if both fall**, because the
short leg gains while the long leg loses less (and vice-versa).

Open both legs -- a long and a short -- with whatever order types you prefer (here:
a resting limit on the long, a market fill on the short):

```{r pairs}
# Leg 1: LONG BTC (limit).
trading$place_order(
  name = "BTC", is_buy = TRUE, sz = 0.002, limit_px = 62000,
  order_type = list(limit = list(tif = "Gtc"))
)

# Leg 2: SHORT ETH (market).
trading$market_open(name = "ETH", is_buy = FALSE, sz = 0.4)
```

Once filled, the account holds the two opposing legs. `get_positions()` returns one
row per open position, with a signed `szi` (positive = long, negative = short):

```{r positions}
account <- HyperliquidAccount$new(keys = KEYS)
account$get_positions()[, .(coin, szi, entry_px, position_value, unrealized_pnl)]
```

> On a real testnet run this exact pair filled as **long 0.0002 BTC @ \$64,424**
> and **short 0.01 ETH @ \$1,688.9** -- a balanced spread. The spread's profit and
> loss is the *difference* between the two legs' moves.

## Protecting a position: take-profit and stop-loss

A **trigger order** fires when the market reaches a `triggerPx`. Use `tpsl = "tp"`
to take profit, `tpsl = "sl"` to stop a loss; `isMarket = TRUE` fills at market
once triggered. Make it `reduce_only` so it can only *close* the position.

```{r tpsl}
# Stop-loss on the BTC long: if BTC trades down to 60,000, market-sell to exit.
trading$place_order(
  name = "BTC", is_buy = FALSE, sz = 0.002, limit_px = 60000,
  order_type = list(trigger = list(isMarket = TRUE, triggerPx = 60000, tpsl = "sl")),
  reduce_only = TRUE
)
```

## Monitoring and closing

Check your fills, then flatten each leg with `market_close()` (a reduce-only
market order sized to the open position).

```{r close}
# Most recent fills.
head(account$get_user_fills(), 3)

# Close both legs of the pair.
trading$market_close(name = "BTC")
trading$market_close(name = "ETH")
```

## Putting it together

- `is_buy = TRUE` longs, `is_buy = FALSE` shorts -- both first-class.
- Choose the order type to control execution: limit + `Gtc`/`Ioc`/`Alo`, or market.
- A pairs trade is just **a long and a short held together**, profiting from the
  spread and shrinking exposure to the overall market.
- Bracket positions with `reduce_only` trigger orders (TP/SL), and size with
  leverage you can survive.

For the full account and market-data surface, see the
[Getting Started](getting-started.html) guide; for the real funded round-trip and
its pitfalls, see the [live testnet walkthrough](live-testnet-walkthrough.html).
